Coherent optical association of a single molecule

### 2020-09-24 paper.tex
Update on Overleaf.

In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), we consider the initial atomic state, an excited intermediate state, and the target weakly-bound molecular state in the ground electronic potential. The initial atomic state and target weakly-bound state are coupled by two photons, $\Omega_a$ and $\Omega_m$ to the excited intermediate state, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The Raman Rabi Rate for a detuned transfer, $ \Omega_a\Omega_m / 2\Delta$ depends on both of these matrix elements and the single photon detuning. Unlike for Raman transitions in atoms, the two matrix elements, $ \Omega_m$ and $ \Omega_a$ are greatly imbalanced. Since $ \Omega_m $ is generally much larger than $ \Omega_a $ due to the wavefunction mismatch between the atomic state and the excited molecular state, the scattering rate predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth. We choose the power of the Raman beams to be equal (which gives the largest Raman Rabi rate at a fixed total power), so there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning. Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, larger detuning is preferred.

>>>>

In a simplified model of a three-level system (as shown in Fig.~\ref{f-theory}), we consider the initial atomic state, the target weakly-bound molecular state coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with single photon detuning $ \Delta $, and two photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The Raman Rabi Rate for a detuned transfer, $ \Omega_a\Omega_m / 2\Delta$ depends on both of these matrix elements and the single photon detuning. Unlike for Raman transitions in atoms, the two matrix elements, $ \Omega_m$ and $ \Omega_a$ are greatly imbalanced. Since $ \Omega_m $ is generally much larger than $ \Omega_a $ due to the wavefunction mismatch between the atomic state and the excited molecular state, the scattering rate predominantly comes from the molecular state, $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth. We choose the power of the Raman beams to be equal (which gives the largest Raman Rabi rate at a fixed total power), so there is an additional factor of 2 in the scattering rate, since the molecular state scatters off of both Raman beams at roughly the same single photon detuning. Thus, the ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, larger detuning is preferred.
